Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-18 paper/main.tex
results: rearrange blocks of text

\begin{itemize}

    \item Zwischenüberschriften rausnehmen, wenn Struktur so in Ordnung

    \item revise captions of Table 1 + 3 (regressors based on annotation of
    the other FG stimulus are now dropped from the table but mentioned in
    section "statistial model / contrasts")

\end{itemize}

@@

\begin{itemize}
\item adjust structure of results to structure of discussion
\item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
    wurde
\end{itemize}

@@

@@

\section{Results}
\todo[inline]{we have to decide how we want to present this: a) by stimulus or b) by analysis type. With the present abstract I am leaning towards (a), but we should debate that}

@@

\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; imo it is
important that we do not have clusters all over the brain}

@@

\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
das viel näher liegende places vs faces? COH: should at least be clearer after
revision of method section}

@@

\subsection{Group results}

\subsubsection{AD: PPA in primary contrast}

% intro
First on a group average level, we tested if results of a whole-brain analysis
based on the audio-description's annotation would lead to increased hemodynamic
activity in the PPA.
% primary AD contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, the clusters of the current analysis are at the borders of the
posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
lingual gyrus.
% precuneus
Two additional clusters are located in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

% table group results primary AD contrast
\begin{table*}[t]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

% figure group results primary AD & AV contrasts
\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns to non geometry-related nouns spoken by
        the audio-description's narrator (\texttt{geo, groom > all non-geo})
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a new setting with cuts to a familiar perspective
        (\texttt{vse\_new > vpe\_old})
   \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

\subsubsection{AD: robustness of PPA across contrasts}

@@

% figure group results of robustness across all AD & AV contrasts
\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).}
    \label{fig:stability-slices}
    \end{figure*}

\paragraph{AD: other significant clusters across contrasts}
% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list; depends on the discussion I guess;
anyhow: clusters are not ``random'' but make sense which speaks for the use of
naturalistic stimuli}

@@

\subsubsection{AV: PPA in primary contrast}
% AV intro
As conceptual/cross-modal control of the group average results, we also analyzed
data from the audio-visual movie by contrasting different kinds of movie cuts
independent(ly) from the frames' visual content following the cut.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises, parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

\begin{table*}[t]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

\subsubsection{AV: robustness of PPA across contrasts}

\paragraph{AV: other significant clusters across contrasts}

\subsubsection{AD \& AV: (negative) control contrasts}

@@

\subsection{individual results}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of audio-description's primary
        $t$-contrast (blue) that compares geometry-related nouns to non
        geometry-related nouns spoken by the audio-description's narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to new setting with cuts
        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the AV stimulus
        in sub-09 and sub-18, and voxels of right cluster of the AV stimulus in
        sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

\begin{figure*} \centering
    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AD stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right).
        The overlays depict voxels spatially contrained to be located in the
        temporal and occipital cortex (gray),
        PPA overlap of all subjects (blue),
        and individual PPA(s) (red).}
    \label{fig:bland-altman} \end{figure*}

>>>>

\begin{itemize}
    \item Zwischenüberschriften rausnehmen, wenn Struktur so in Ordnung
    \item revise captions of Table 1 + 3 (regressors based on annotation of
    the other FG stimulus are now dropped from the table but mentioned in
    section "statistial model / contrasts")
\end{itemize}

@@

\begin{itemize}
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
    wurde
    \item location of tables \& figures is pretty confusing at the moment
\end{itemize}

@@

\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
das viel näher liegende places vs faces? COH: places vs. face = simple set in
Sengupta; here, we follow the strict set used in Sengupta; tbh, not mentioned in
detail}

@@

\section{Results}

@@

\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; COH: imo it is
important that we do not have clusters all over the brain}

@@

@@

\subsection{Primary contrasts}

% intro
First on a group average level, we tested if results of a whole-brain analysis
based on the audio-description's annotation would lead to increased hemodynamic
activity in the PPA.

\subsubsection{group}
% AV intro
As conceptual/cross-modal control of the group average results, we also analyzed
data from the audio-visual movie by contrasting different kinds of movie cuts
independent(ly) from the frames' visual content following the cut.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises, parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

% AD
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, the clusters of the current analysis are at the borders of the
posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
lingual gyrus.
% precuneus
Two additional clusters are located in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

% figure group results primary AD & AV contrasts
\begin{figure*}[h!] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns to non geometry-related nouns spoken by
        the audio-description's narrator (\texttt{geo, groom > all non-geo})
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a new setting with cuts to a familiar perspective
        (\texttt{vse\_new > vpe\_old})
   \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

% table group results primary AD contrast
\begin{table*}[h!]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

\subsubsection{individuals}

\todo[inline]{make focus on AD clearer}

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of audio-description's primary
        $t$-contrast (blue) that compares geometry-related nouns to non
        geometry-related nouns spoken by the audio-description's narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to new setting with cuts
        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the AV stimulus
        in sub-09 and sub-18, and voxels of right cluster of the AV stimulus in
        sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

\begin{figure*}[h!]
\centering
    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AD stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right).
        The overlays depict voxels spatially contrained to be located in the
        temporal and occipital cortex (gray),
        PPA overlap of all subjects (blue),
        and individual PPA(s) (red).}
    \label{fig:bland-altman}
\end{figure*}

\subsection{Robustness of PPA across contrasts}

\subsubsection{AV}

\subsubsection{AD}

@@

% figure group results of robustness across all AD & AV contrasts
\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).}
    \label{fig:stability-slices}
\end{figure*}

\subsection{Non-PPA clusters across contrasts}

% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list; depends on the discussion I guess;
anyhow: clusters are not ``random'' but make sense which speaks for the use of
naturalistic stimuli}

\subsubsection{AV}

\subsubsection{AD}

@@

\subsection{control contrasts (AV \& AD)}

@@
